### 2021-07-10 submission.tex
Q4 finished

\section*{Question 4} 
\begin{enumerate}[label = (\alph*)]
    \item
    \begin{enumerate}[label = (\roman*)]
    \item

    \item

@@

	\item
    \begin{enumerate}[label = (\roman*)]
    \item

    \item

@@

	\item
    \begin{enumerate}[label = (\roman*)]
    \item

    \item

    \item

    \item

@@

>>>>

\section*{Question 4} 
\begin{enumerate}[label = (\alph*)]
    \item
    \begin{enumerate}[label = (\roman*)]
    \item
    Let's define an auxiliary function $J_w = \begin{cases}
      1, & \text{if} \; w \; is \; drawn \\
      0, & \text{otherwise}
    \end{cases}$

    The number of unique tokens X is equal to:

    $X = \sum_{w=1}^{|V|} J_w$

    Using the linearity of expectations, the expected value of X is equal to:

    $E[X] = E[\sum_{w=1}^{|V|} J_w] = \sum_{w=1}^{|V|} E[J_w]$

    where:

    $E[j_w] = P(J_w = 1) = P(at \;least\; one\; w \;selected) = 1 - P(w \; not \; selected) = 1- \frac{|V|-1}{|V|}$

    Finally: $X = |V| \cdot (\frac{|V|-1}{|V|})^n$

    \item
    P(all words appear) = 1 - P(at least one w doesn't appear) = $1 - (P(!w_1) \bigcup P(!w_2) \bigcup ... \bigcup P(!w_|V|) = 1 - |\bigcup_{i=1}^{|V|}P(!w_i)|)$

    where '!' denotes that the word is not selected. 
    The above union can be found using the inclusion-exclusion principle.

    $|\bigcup_{i=1}^{|V|}P(!w_i)| = \sum_{J \in \{1,...,|V|\}} (-1)^{|J|+1}|\bigcup_{j \in J}P(!w_i)|) = $

@@

	\item
    \begin{enumerate}[label = (\roman*)]
    \item
    A - expected additional draws if just selected any word other than 'work'

    B - expected additional draws if just selected 'work'

	A is equal to the initial draw + P(w != 'hard') * A + P(w = 'hard') * B, what yields:

	$A = 1 + \frac{|V|-1}{|V|} \cdot A + \frac{1}{|V|} \cdot B$

	B is equal to one draw in case that we select word 'hard' + P(w != 'hard') * A, what yields:

	$B = 1 + \frac{|V|-1}{|V|} \cdot A$

	Solving the above system of equations in terms of A, we get:

	$A = \frac{|V|^2-1}{|V|-1}$

    \item
    TO DO

@@

	\item
    \begin{enumerate}[label = (\roman*)]
    \item
    A - expected number of draws before the first selection

    B - expected additional number of draws after at least one word has been selected.

    A is equal to B + the initial draw:

    $A=B+1$

    B is equal to P(w is the same as the previous one) + P(w is different) * A:

    $B = \frac{1}{|V|} + \frac{|V|-1}{|V|} \cdot A$

    The solution of the above set of equations in terms of A is:

    $A = |V|+1$

    \item
    I assume that the input is an integer corresponding to a given word index.

    $w_0=1$

    $w_1=-1$

    $w_2=0$

    $w_0=0$

    $b_0=0$

    $f(x)=\begin{cases}
      1, & \text{if} \; x=0\\
      0, & \text{otherwise}
    \end{cases}$

    $g(x) = x$

    \item
    $w_3=1$

    $w_4=1$

    $w_5=1$

    $b_2=0$

    $b_0=0$

    $g(x) = x$

    $h(x) = x$

    A non-linear activation is required because the output cannot be express as a linear function of the inputs. It is similar to the XOR problem.

    \item
    A non-uniform has a yields greater chances of sequentially drawing the same token. 
    In can be intuitively depicted using an extreme case, when always the same word is drawn.

@@

\section*{Question 5} 
\begin{enumerate}[label = (\alph*)]
    \item
    \begin{enumerate}[label = (\roman*)]
    \item

	\end{enumerate}
\end{enumerate}
